---
title: "Untitled"
author: "kuaifang liang"
date: "12/1/2019"
output:
  word_document: default
  html_document: default
---
```{r}
library(lattice)
library(foreign)
library(MASS)
library(car)
require(stats)
require(stats4)
library(KernSmooth)
library(fastICA)
library(cluster)
library(leaps)
library(mgcv)
library(rpart)
library(pan)
library(mgcv)
library(DAAG)
library(TTR)
library(tis)
require(datasets)
require(graphics)
library(forecast)
library(stats)
library(TSA)
library(timeSeries)
library(fUnitRoots)
library(fBasics)
library(tseries)
library(timsac)
library(TTR)
library(fpp)
library(strucchange)
library(vars)
library(lmtest)
library(dlnm)
library(KFAS)
library(FKF)
#install.packages(vars)
library(vars)
library(strucchange)
#install.packages("greybox")
library(greybox)
```


```{r}
#read data
data=read.csv("22.csv",header = TRUE)
attach(data)
V1=data$Coal.Consumption.for.Electricity.Generation.and.Useful.Thermal.Output..Industrial.Sector
V2=data$Petroleum.Consumption.for.Electricity.Generation.and.Useful.Thermal.Output..Commercial.Sector
#convert data into time series
a_ts<-ts(V1,start=1989,freq=12)
b_ts<-ts(V2,start=1989,freq=12)
t<-seq(1989,2018,length=length(a_ts))
plot(a_ts,main="Coal.Consumption.for.Electricity.Generation.and.Useful.Thermal.Output..Industrial.Sector")
plot(b_ts,main="Petroleum.Consumption.for.Electricity.Generation.and.Useful.Thermal.Output..Commercial.Sector")
```

(1)
```{r}
# Plot time series--Coal Consumption for Electricity Generation and Useful Thermal Output, Industrial Sector
tsdisplay(a_ts,main="Coal Consumption in Industrial Sector")
# Plot time series--Petroleum Consumption for Electricity Generation and Useful Thermal Output, Commercial Sector
tsdisplay(b_ts,main="Petroleum Consumption in Commercial Sector")
```
Coal Consumption in Industrial Sector: ACF decays to 0 very slow, which means that the data may have strong time dependence. We cannot get much information from PACF since it is very random.
Petroleum Consumption in Commercial Sector: We can know data has strong time dependence from ACF because it decays slowly and all time period has spike. However, we cannot get much information from PACF since it is very random.


(2)
```{r}
# Fit an Arima model
auto.arima(a_ts,xreg = t)
# ARIMA(1,0,1)(2,0,0)[12]Drift--Coal Consumption in Industrial Sector
a=Arima(a_ts,order = c(1,0,1), seasonal = c(2,0,0),xreg = t)
summary(a)
coeftest(a)
plot(t,a$fitted,type="l")
lines(a_ts,col="red")

# ARIMA(1,0,2)(2,0,0)[12]Drift--Petroleum Consumption in Commercial Sector
auto.arima(b_ts,xreg = t)
b=Arima(b_ts,order = c(1,0,2), seasonal = c(2,0,0),xreg = t)
summary(b)
coeftest(b)
plot(t,b$fitted,type="l")
lines(b_ts,col="red")
```
For the coal consumption series, we use auto.arima to find that the model should be ARMA(1,1) with S-AR(2),S=12. The graph shows that the beginning of the data fit well but the end of data does not fit very well. But the coeffients are statistically significant.
For the petroleum consumption series, the auto.arima shows that the model should be ARMA(1,2) with S-AR(2),S=12. The graph shows that the data are not perfectly fit but changing trend is smiliar to the orginal data.


(3)
```{r}
# Fit a trend--Coal Consumption in Industrial Sector
# Linear
t1.1=lm(V1~t)
summary(t1.1)
# Linear-qudratic 
t2=t^2
t1.2=lm(V1~t+t2)
summary(t1.2)

AIC(t1.1,t1.2)
BIC(t1.1,t1.2)
# quadratic trend is the fittest for coal consumption in industrial sector.
```
After comparing two trend models, we choose Linear-qudratic as the most fitted trend for coal consumption.


```{r}
# Fit a trend--Coal Consumption in Industrial Sector
# Linear
t2.1=lm(V2~t)
summary(t2.1)
# Linear-qudratic 
t2=t^2
t2.2=lm(V2~t+t2)
summary(t2.2)

AIC(t2.1,t2.2)
BIC(t2.1,t2.2)
# log-quadratic-period trend is the fittest for petroleum consumption in commercial sector.
```
After comparing two models, we choose linear model for petroleum consumption since BIC of linear model is lower.


```{r}
#Fit a quadrtaic trend + seasonality model
s1.1=tslm(a_ts~t+t2+season)
summary(s1.1)
acf(s1.1$res,lag=36)
pacf(s1.1$res,lag=36)

s2.1=tslm(b_ts~t+t2+season)
summary(s2.1)
acf(s2.1$res,lag=36)
pacf(s2.1$res,lag=36)
# The residuals + ACF and PACF suggest cycles.
```
For coal consumption, the seasonal factors are statistically significant in Feburary, April and May. For petroleum consumption, the seasonal factors are statistically significant and from ACF plot, we can also know that petroleum consumption has strong seasonality. But ACF and PACF are not show residuals are white noise yet, suggesting we may not include cycle.


```{r}
# fit model for coal consumption in industrial sector
# Model: Trend + Cycles + Seasonality
m1=Arima(a_ts,order=c(1,0,1),seasonal=list(order=c(2,0,0)),include.drift = T)
summary(m1)
coeftest(m1)

# Look at the ACF and PACF
acf(m1$residuals,lag=36)
pacf(m1$residuals,lag=36)
Box.test(m1$residuals)
# Judging from acf and pacf graph, we find that the resiudals seem a like white noise.
```
ACF and PACF showed no spikes and box-test showed the residuals are white noise.


```{r}
# fit model for coal consumption in industrial sector
# Model: Trend + Cycles + Seasonality
auto.arima(b_ts)
m2=Arima(b_ts,order=c(1,0,2),seasonal=list(order=c(2,0,0)),include.drift = T)

acf(residuals(m2),lag=36)
pacf(residuals(m2),lag=36)
Box.test(m2$residuals)
# Though the acf and pacf don't perform well, we find that the residuals is white noise by using box-test.
```
ACF and PACF showed some spikes but box-test still showed the residuals are white noise.

(4)
```{r}
# Residuals plot
plot(m1$residuals,ylim=c(-1000,1000))
plot(m2$residuals,ylim=c(-1000,1000))

# Fitted value plot
plot(a_ts,ylab="consumption", xlab="Time", lwd=2, col='gray',type="l",main="Fitted value vs. real value--Coal")
lines(fitted(m1),col="green")

plot(b_ts,ylab="consumption", xlab="Time", lwd=2, col='gray',type="l",main="Fitted value vs. real value--Petroleum")
lines(fitted(m2),col="red")
```
The two residuals plots show that the residuals fluctuate around 0 with little volatility. 
For the fitted-value plot, it looks like the fitted-value are nearly matched with real value, which means our models are good fit for the data.

(5)
```{r}
# Plot acf and pacf--Coal
acf(m1$residuals,lag=36)
pacf(m1$residuals,lag=36)

# Plot acf and pacf--Petroleum
acf(m2$residuals,lag=36)
pacf(m2$residuals,lag=36)
```
For coal consumption:ACF and PACF showed no spikes and box-test showed the residuals are white noise.
For petroleum consumption: ACF and PACF showed some spikes but box-test still showed the residuals are white noise.


(6)
```{r}
# CUSUM plot--Coal
plot(efp(m1$residuals~1, type='Rec-CUSUM'))

# CUSUM plot-Petroleum
plot(efp(m2$residuals~1, type='Rec-CUSUM'))

# Standardized residuals are within boundary. Thus, our models perfrom well.
```
Both CUSUM test results are good and our residuals are relatively stable.

(7)
```{r}
# Recursive residuals plot--Coal
resm1=recresid(m1$res~1)
plot(resm1,ylim=c(-600,600),main="Recursive residuals--Coal, Industrial Sector")

#Recursive residuals plot--Petroleum
resm2=recresid(m1$res~1)
plot(resm2,ylim=c(-600,600),main="Recursive residuals--Petroleum, Commercial Sector")
```
Both recursive residuals look good.

(8)
```{r}
# Diagnostic statistics of Coal, Industrial Sector
summary(m1)
coeftest(m1)
summary(m2)
coeftest(m2)
```
the coefficients of two Arima models are statistically significant.

(9)
```{r}
m1_f=forecast(m1,h=12)
plot(m1_f)
m2_f=forecast(m2,h=12)
plot(m2_f)
```
Two forecasts are basically fit the expectation through rough trends,seasonalities and cycles.

(10)
```{r,fig.width=8, fig.height=8}
library(car)
df =data.frame(a_ts, b_ts)
VARselect(df, lag.max=10)
var1 = VAR(df,2)
S(var1)
plot(var1)
```
From VAR model, we can see the coal consumption fit the petroleum consuption better and the residual of coal consumption is nearly covariance stationary. The residual of petroleum is not very stationary.

(11)
```{r}
irf(var1)
plot(irf(var1))
```
From IRF graphs, we can see coal consumption has an effect on petroluem consumption but petroleum consumption has little effect on coal consumption 

(12)
```{r}
grangertest(a_ts, b_ts)
grangertest(b_ts, a_ts)
```
From the Granger-Causality test for coal consumption, the test results show that we reject the hypothesis that coal consumption has no effect on petroleum consumption, meaning that coal consumption has a significant effect on petroleum.


(13)
```{r}
var.predict = predict(object=var1, n.ahead=12)
plot(var.predict)
```
This VAR model including only its own lagged terms and the lagged terms of another variable is too simple. Its prediction effect is not very good compared with the ARIMA model.

14
(a)
```{r}
# Recursive Backtest 12-step ahead

# forecast 
model_l = "forecast(m1,h = h,level=95)"
model_h = "forecast(m2,h = h,level=95)"
ourValue = "mean"

# separation : training 288  test 72
V12rec = ro(a_ts,h=12,origins = 61,call=model_l,value=ourValue,
                     ci=F,co=T)
V1rec = ro(a_ts,h=1,origins = 72,call=model_l,value=ourValue,
                    ci=F,co=T)
V12rol = ro(a_ts,h=12,origins = 61,call=model_l,value=ourValue,
                   ci=T,co=T)
V1rol = ro(a_ts,h=1,origins = 72,call=model_l,value=ourValue,
                  ci=T,co=T)
V22rec = ro(b_ts,h=12,origins = 61,call=model_h ,value=ourValue,
                     ci=F,co=T)
V2rec = ro(b_ts,h=1,origins = 72,call=model_h ,value=ourValue,
                    ci=F,co=T)
V22rol = ro(b_ts,h=12,origins = 61,call=model_h ,value=ourValue,
                   ci=T,co=T)
V2rol = ro(b_ts,h=1,origins = 72,call=model_h ,value=ourValue,
                  ci=T,co=T)

# MAPE over each step for recursive f12
l_f12_MAPE_eachstep = apply(abs((V12rec$mean-V12rec$holdout)
                                /V12rec$holdout),1,mean)
l_f12_MAPE_eachiteration = apply(abs((V12rec$mean-V12rec$holdout)
                                     /V12rec$holdout),2,mean)
plot(l_f12_MAPE_eachstep, main='CoalRecursive 12-step MAPE each step')
plot(l_f12_MAPE_eachiteration, main='Coal Recursive 12-step MAPE each iteration')


h_f12_MAPE_eachstep = apply(abs((V22rec$mean-V22rec$holdout)
                                /V22rec$holdout),1,mean)
h_f12_MAPE_eachiteration = apply(abs((V22rec$mean-V22rec$holdout)
                                     /V22rec$holdout),2,mean)
plot(h_f12_MAPE_eachstep, main='Petroleum Recursive 12-step MAPE each step')
plot(h_f12_MAPE_eachiteration, main='Petroleum Recursive 12-step MAPE each iteration')

```

(b)
```{r}
# Recursive Backtest 1-step ahead
# APE over each iteration for recursive f1
l_f1_recursive_APE_eachiteration = abs(V1rec$mean-V1rec$holdout)/V1rec$holdout
l_f1_recursive_APE_eachiteration = t(l_f1_recursive_APE_eachiteration)
plot(l_f1_recursive_APE_eachiteration, main='Coal Recursive 1-step APE each iteration')

h_f1_recursive_APE_eachiteration = abs(V2rec$mean-V2rec$holdout)/V2rec$holdout
h_f1_recursive_APE_eachiteration = t(h_f1_recursive_APE_eachiteration)
plot(h_f1_recursive_APE_eachiteration, main='Petroleum Recursive 1-step APE each iteration')

```

(c)
As can be seen from the two figures above, our model performs better in the shorter horizon because we find that MAPE on shorter horizon is shorter horizon than longer horizon on average.

(d) 
```{r}
# Rolling Backtest 12-step ahead

# forecast error over each iteration for rolling f12
l_f12_rolling_FE_eachiteration = V12rol$mean-V12rol$holdout
h_f12_rolling_FE_eachiteration = V22rol$mean-V22rol$holdout

# forecast error over each interation for rolling f1
l_f1_rolling_FE_eachiteration = V1rol$mean-V1rol$holdout
l_f1_rolling_FE_eachiteration = t(l_f1_rolling_FE_eachiteration)
plot(l_f1_rolling_FE_eachiteration)

h_f1_rolling_FE_eachiteration = V2rol$mean-V2rol$holdout
h_f1_rolling_FE_eachiteration = t(h_f1_rolling_FE_eachiteration)
plot(h_f1_rolling_FE_eachiteration)
```


(e)
We find that the errors found using a recursive backtesting scheme compared with the errors observed using a moving average backtesting scheme is almost the same.Therefore, the two prediction methods are not different for us.

